% \documentclass[12pt]{article}
\documentclass{article}
\usepackage{xr}
\usepackage{physics}
\usepackage{float}
\usepackage{tabularray}
\UseTblrLibrary{booktabs}
\usepackage[
    backend=biber,
    style=apa
]{biblatex}

% Equations
\input{equations}

% Tables
\input{tables}

% References
\addbibresource{references.bib}

% Title
\title{
    Introduction to Quantitative Career Matching:\\
    How to Statistically Pick the Right Occupation
}
\author{Cao Bittencourt}
\date{\today}

\begin{document}

\maketitle

\newpage

% Abstract
\begin{abstract}
    \noindent
    In this introductory paper, we address the crucial, but highly neglected, subject of data-driven career choice and development. We begin by sketching out the most basic approach to quantitative career matching, and test our model by calculating career compatibility coefficients with data from the United States' primary source of occupational information, the O*NET framework. We, then, illustrate the results with a sample of occupations from O*NET's database, and describe the best matches for each selected career. Despite the model's simplicity, we found career matches to be very accurate, although not as precise as they would be had we employed superior methods. In the future, we expect to cover some advanced material, deliberately left out of this introduction, and detail more sophisticated and performant models.\\

    \noindent
    \textbf{Keywords:} Career matching; Career compatibility; Career choice; Career development; Vocational choice; Occupational Information Network.
\end{abstract}

% Table of contents
\newpage
\tableofcontents

% List of tables
\newpage
\listoftables

% Introduction
\newpage
\section{Introduction}
Choosing the right occupation is one of the most important decisions in life.
In fact, a considerable portion of a person's life -- generally, a third of it
-- is actually spent working. Additionally, finding a career that is suitable
for one's skill set and natural aptitudes greatly impacts job performance and
overall satisfaction. Having sufficient compensation to feed a family, and
adequate work-life balance, are also crucial. And, for some individuals, we
could even cite self-fulfillment and ethical reasons as major factors
contributing to the significance of work.

Given this overarching importance of career choice and development, we would
expect to find many quantitative approaches to the issue in the scientific
literature. Nonetheless, despite some competent efforts by psychometricians and
personality theorists
\parencites[e.g.][]{holland1959theory, holland1997making}{schein1978careerdynamics,
    schein1993careeranchors}, not much has been done to address this problem in a
purely data-driven manner.

In the late 1990s, however, a notable achievement in this area was brought
about by the Occupational Information Network \parencite{onet1998data}. Sponsored by the United States Department of Labor, this
program set out to quantify job requirements in a standardized fashion. Their
research resulted in a robust database of career paths, which includes numeric
estimates of competence levels for dozens of abilities; as well as several
other characteristics, such as the frequency of typical work activities, the
seriousness of expected job hazards, etc. Their catalog of occupations is vast,
and their data have been updated frequently for over two decades.

But even with such rich information publicly available, there is still a lack
of statistical modeling of it. In this series of articles, we aim to fix this.
Starting with the most immediate concepts, we expect to document all
mathematical methods we have devised to tackle the study of career choice and
development. Here, we detail a basic approach to quantitative career matching
based on the estimation of compatibility scores. In the future, we shall cover
more complex matching algorithms, and advanced topics, like identifying
occupations' core attributes, assessing the generality of career paths (to
distinguish between generalist and specialist workers), calculating
employability coefficients, constructing optimal strategies for career
planning, talent acquisition, and much more.

% Methods
\section{Methods}
\subsection{The Occupational Information Network}
The Occupational Information Network (O*NET) is an American primary source of
occupational information. It was developed during the mid 1990s, and published
in 1998, by a team of public and private sector organizations, in partnership
with the Department of Labor's Employment and Training Administration. Its aim
is to facilitate the maintenance of a skilled workforce through the collection
and dissemination of occupational data \parencites{mariani1999onet}{onet2024about}.

Essentially, the O*NET model provides a thorough, quantitative, description of
hundreds of SOC \parencite[Standard Occupational Classification, see][]{bls2018soc} career paths in
a vectorized format. O*NET accomplishes this task by systematically evaluating
the competencies of actual people in the labor market, on a 0 to 100 scale, in
order to derive numeric guidelines on what attributes are required for each
position.

Therefore, the resulting ``career profiles" from O*NET's surveys are meant to
be taken as ``canonical representations" of SOC occupations: they ``map out"
what, say, an engineer, an accountant, or any other occupation tends to ``look
like", in terms of professional attributes.

\subsection{Skill Sets}
With the convenient structure of the O*NET framework in mind, we begin by
defining and measuring the professional attributes that characterize each
economic agent in the labor market. To do so, we establish a bounded, uniform
scale from 0 (complete incompetence) to 100 (complete mastery), such that:
\EqnAttribute where $a_{i}^{k}$ is the $i$-th professional attribute of a
person $k$. Moreover, let us denote as a ``skill set", or ``career profile",
the vector of their $m$ attributes, like so: \EqnSkillSet

Thus, all individuals in the economy -- whether employed, or not -- are
mathematically described by their own skill sets, or career profiles; and this
applies to regular SOC occupations as well, like the ones included in the O*NET
database.

\subsection{A Euclidean Approach to Career Matching}
Finally, individuals and occupations are said to be similar to the exact degree
to which their vectors of professional attributes, or skill sets, overlap.

To measure this compatibility, we can utilize several matching methods. Some of
these are complicated, and require lengthy explanations, while others are much
easier to introduce. As the scope of this article is very limited, we only
cover the most basic of methods: the Euclidean approach to career matching.

\subsubsection{An Initial Model for Euclidean Career Matching}
In this approach to career matching, compatibility is estimated by the inverse
function of Euclidean distance. Hence, we first define this concept:
\EqnEuclideanDistance

Equation (\ref{eqn:euclidean_distance}) measures the absolute distance from the
professional attribute vector $\boldsymbol{a_{\boldsymbol{k}}}$ to a comparison
vector $\boldsymbol{a_{q}}$; in other words, it tells us how these two skill
sets are \textit{dissimilar}.

But, of course, our interest here is career compatibility, not its opposite.
Furthermore, similarity is typically expressed as a percentage; and for this,
we need dissimilarity to be bounded to a known interval. Therefore, in order to
convert the Euclidean distance (\ref{eqn:euclidean_distance}) to a similarity
metric, we need to employ some sort of normalization procedure, like the
following: \EqnNormalizedDistance

The denominator in equation (\ref{eqn:normalized_distance}) is the maximum
theoretical distance to the $\boldsymbol{a_q}$ comparison skill set. That is,
here we normalize distance (\ref{eqn:euclidean_distance}) by calculating the
distance to $\boldsymbol{a_q}$ from its most dissimilar vector. So, for each
coordinate of the $\boldsymbol{a_{q}}$ skill set, we measure which distance
would be greater: that from the scale's lower bound (viz. 0), or that from the
upper bound (viz. 100), as any other distance has to be less than those to the
scale's limits. This way, the denominator corresponds to the maximum distance
to $\boldsymbol{a_{q}}$; and, consequently, the normalized distance
$\tilde{d}(\boldsymbol{a_{\boldsymbol{k}}}, \boldsymbol{a_{q}}) \in [0,1] \
    \forall \ \boldsymbol{a_{\boldsymbol{k}}}, \boldsymbol{a_{q}}$.

At last, similarity is easily derived from the normalized dissimilarity:
\EqnSimilarity

As opposed to equations (\ref{eqn:euclidean_distance}) and
(\ref{eqn:normalized_distance}), this formula describes the measure to which
career profiles are \textit{similar}. Again, it is evident
$s(\boldsymbol{a_{\boldsymbol{k}}}, \boldsymbol{a_{q}}) \in [0,1] \ \forall \
    \boldsymbol{a_{\boldsymbol{k}}}, \boldsymbol{a_{q}}$. Thus, we can estimate, as
a percentage, how compatible a person is with an occupation, and whether they
are alike in terms of their competencies, or not.

\subsubsection{A Weighted Euclidean Approach to Career Matching}
Although straightforward, the above method is far too simplistic, for each and
every competency is given the same importance in matching; and this is,
clearly, not reasonable. In reality, some professional attributes are,
definitely, more important to some occupations, while to others they are less
or even not important.

Consider, for instance, the absurdity of a barber who knows a lot about the
arts, and fashion, and entertaining customers, and even accounting and
bookkeeping, and yet does not know how to actually cut hair. One could call
them artistic, or stylish, but hardly a barber. For despite the usefulness of
all these other things for the barber, they are not nearly as important as
their main activity (viz. cutting hair).

This is the issue of weighting professional competencies, and it is crucial for
adequate career matching. In fact, to the degree to which attributes are said
to be ``central", or ``indispensable", to certain career paths (like being able
to cut hair is for a barber), so too weighting these attributes is
indispensable for career matching algorithms to function properly.

Now, as it is with matching methods, here also we find a variety of manners of
weighting professional attributes. The first, which we cover below, is to use
linear weights. This said, quadratic, logistic, or any sort of increasing
weights can be employed as well. In our more complex career matching
algorithms, for example, we make use of a specific function to determine skill
sets' core competencies, and weight them accordingly, so as to significantly
improve models' performance. For illustrative purposes, however, linear weights
seem to suffice.

\subsubsection{Linear Weights for Euclidean Career Matching}
When implementing linear weights with the Euclidean approach, each distance
between career profiles is multiplied by the attributes of the comparison skill
set (viz. that to which compatibility is to be calculated). Thus, distances to
the most important competencies are emphasized, while the remaining receive
less importance.

Mathematically, the weighted metrics (with subscript $w$) for similarity scores
and normalized distances are as follows: \EqnWeightedSimilarity where
\EqnWeightedDistance

With these adjusted equations, Euclidean distance is weighted proportionally to
the professional attribute levels of the $\boldsymbol{a_{q}}$ career profile.
This means that the matching method is optimized for every comparison skill
set, as irrelevant competencies are left out of the analysis, and the
``indispensable" ones (e.g. cutting hair for a barber, dentistry for a dentist)
are given their full importance.

\subsubsection{Adjusting for Overqualification}
A positive side effect of the use of weights in career matching is an implicit
correction for the statistical penalties of overqualification. These arise, in
the original approach, whenever an individual has additional competencies from
other fields that are not required at a certain position, and cause the
unadjusted distance (\ref{eqn:normalized_distance}) to yield less favorable
similarity estimates. For, if $a_{i}^{k} > a_{i}^{q}$, then
\EqnDistanceDerivative

This overqualification problem is highly detrimental for matching accuracy, as
it tends to ``punish" people with many professional attributes, whether they
are skilled generalists or merely hobbyists. But, of course, as the absurd
scenario of the useless barber mentioned above, this too is not reasonable at
all. Indeed, no one would say, for instance, that an airline pilot is less of a
pilot if they also know how to cut hair, just as we do not say a barber is less
of a barber if they cannot fly an airplane. Put another way, competencies that
have ``nothing to do" with an occupation should not be a limiting factor to
career compatibility.

The application of matching weights helps to mitigate this, as the less
important competencies are, rightly, given less importance; and those distances
to completely irrelevant attributes (with competence levels of 0) are even
nullified entirely, so that: \EqnUnweightedWeightedDistances

Therefore, if a person has additional, unnecessary, skills, these weighting
techniques provide a correction for the penalties of overqualification,
decreasing the normalized Euclidean distance and increasing compatibility.

\subsection{Data and Implementation}
The version of the O*NET database utilized contains 873 unique career profiles,
even including a few variants on top of SOC occupations. For brevity's sake,
though, they are succinctly described below in terms of general clusters:
\GeneralOccupationalStatistics

As it concerns matching procedures, career compatibility coefficients were
estimated by comparing all available occupations to one another, instead of
matching against human subjects. This was done for eight reasons: to ensure the
model's internal consistency; to avoid potential sampling biases; to have more
reliable ``targets" when assessing accuracy (as individuals' career profiles
tend to be less defined than O*NET's ``canonical skill sets''); in a similar
fashion, to make results more objectively interpretable for the reader; to
simplify this initial model by postponing, for now, the making of a
competence-preference distinction, that shall be needed later on to account for
the fact that one's skills are not always aligned with their preferences;
because matching careers to careers is, essentially, the same as matching
individuals to careers (for both are defined by competency vectors); because
O*NET's 873 occupations already provide a somewhat large sample size for this
type of study; and, of course, because the O*NET data are, themselves, derived
from rigorous labor market surveys, and consequently their career profiles are,
in fact, representative of the skills of real people. So, even though one of
the model's end goals is to help \textit{individuals} find the right career, at
the present moment, we can test these methods ``internally", without resourcing
to further empirical research.

Unfortunately, this also means we cannot show most of our results, as the O*NET
database contains too many career paths, and the scope of an introductory
article does not allow for all their matches to be displayed. Hence, for this
exercise, we only present four occupations: mechanical engineers, physicists,
credit analysts, and dishwashers. These were choosen to illustrate a
``sufficient range'' of careers: two highly qualified STEM occupations, the
first more ``hands-on'' than the latter; one of the simplest roles in the
economy (viz. dishwashers); and the other somewhere in between (viz. credit
analysts). Their main characteristics are summarized in Table
\ref{tab:summary_occupations}. \SummaryOccupations

The career profiles used for matching were composed of three broad categories
of professional attributes from the O*NET framework, namely: ``Skills",
``Abilities", and ``Fields of Knowledge". These three categories combined sum
to exactly 120 competencies, and are detailed in the Appendix. The remaining
categories of attributes (e.g. ``Interests", ``Work Values") do not constitute
``competencies" in the strict sense of the word, so they were not included in
the analysis. Additionally, a few of the original attribute names were changed
to reduce ambiguity (e.g. from ``Design" to ``Industrial Design").

Finally, all calculations were implemented in the R programming language, with
packages we wrote and published to carry out Euclidean matching and other
algorithms \parencite{atlas.match}. The complete scripts and data can be found in an online
repository \parencite{intro_career_matching}.

% Results
\section{Results}

\subsection{Most Compatible Occupations}
Again, despite the small selection of four occupations, there are still too
many career matches to be displayed here. Thus, we only illustrate the results
of the weighted Euclidean approach with the ten most compatible occupations.
\MatchesEngineers \MatchesPhysicists \MatchesCreditAnalysts \MatchesDishwashers

\subsection{Similarity Matrix}
We also found it useful to build a similarity matrix, with which one can easily
compare occupations' compatibility coefficients: \SimilarityMatrix

As noted in the similarity matrix, comparison occupations are on the horizontal
axis, meaning that Table \ref{tab:similarity_matrix} should be read vertically.
This is because the normalization (\ref{eqn:normalized_distance}) and weighting
(\ref{eqn:weighted_distance}) techniques employed imply the characteristic
symmetry of Euclidean distance is, in most cases, lost.

Therefore, the table shows, for example, that mechanical engineers have 62\%
compatibility with dishwashers, while dishwashers have only 38\% compatibility
with mechanical engineers; that is to say engineers are sufficiently qualified
to perform the job activities of dishwashers, but not the other way around.

% Discussion
\section{Discussion}
Assessing the matching results in Tables
\ref{tab:similarity_engineers}--\ref{tab:similarity_dishwashers}, we could say
this Euclidean model is quite accurate: mechanical engineers are matched to ten
other types of engineers; while theoretical physicists are similar to
astronomers, biophysicists, mathematicians, and scientific roles, in general;
credit analysts, adequately, cluster with occupations in the financial
industry; and dishwashers, in turn, have high compatibility with janitors,
cleaners, and so-called ``blue-collar" positions.

When we analyze Table \ref{tab:similarity_matrix}, we find results to be
likewise accurate. Firstly, the STEM career paths are fairly close to one
another, at 80\% similarity. This is expected, since engineers are, in a way,
applied physicists. Dishwashers, on the other hand, are not really similar to
either one, being more compatible with credit analysts. And, finally, credit
analysts, have roughly 60\% similarity with the other three occupations,
indicating they are moderately compatible, and undifferentiated in this
respect. It also stands out, as already mentioned, that the ``highly qualified"
profiles have high compatibility scores with the ``less qualified", or
``simpler", ones, while the reverse is not true.

As regards precision, however, the baseline Euclidean approach to career
matching used in this exercise is evidently suboptimal. For one thing,
similarity scores are too high when comparing mostly unrelated occupations
(e.g. in ``blue-collar'' matches against technical positions). That is, though
the model's matching predictions ``make sense'', the degree of similarity, for
some careers, is grossly overestimated.

Indeed, the compatibility of, say, dishwashers with engineers and physicists is
relatively low, which is realistic; but, at almost 40\%, it is still,
objectively, not low enough. And their similarity with credit analysts is even
worse, with an exaggerated estimate of 54\%. Thus, while it is true that
dishwashers are not highly compatible with any of these occupations, their
similarity with all of them, specially credit analysts, should be much lower.

To a lesser extent, the same applies to credit analysts, as well. For as an
entry-level position in the field of Finance, credit analysts do seem to be
some sort of ``middle ground" between the other selected roles: in fact, their
main job activities are mathematical in nature, yet are neither as demanding
and abstract as those of physicists, nor as direct and concrete as the
repetitive manual labor of dishwashers. So, in this sense, the estimated
compatibility scores are correct. Nevertheless, the actual numeric values of
these similarities are somewhat out of proportion; and more reasonable figures
would be in the range of 40\% to 50\%, around 10\% less than the coefficients
obtained with the Euclidean method.

A second, more encompassing, deficiency of this approach, that could even help
to explain the first one, has to do with factors that we deliberately left out
of the model. Educational attainment, for instance, is one of them, and it
could drastically change matching results, as several career paths have basic
requirements in the form of specific degrees, certifications, years of
experience, and so on and so forth.

Of course, these other aspects are all very important, and a full analysis of
career compatibility should take them into consideration. That being said, here
we decided to exclude them for two main reasons. The first is that adding such
variables alongside the 120 competencies without modification to the matching
method does not work, in purely practical terms, because the algorithm employed
is not suitable to perform binary filtering based on key, necessary conditions,
but rather to compute the distance between vectors.

The second reason is that these requirements are, actually, best conceptualized
as \textit{independent} coefficients themselves, that can, then, be multiplied,
or otherwise combined with any kind of function to limit career compatibility
scores. Moreover, skill set similarity, the sole object of this initial model,
does not imply -- or is even implied by -- educational attainment, years of
experience, etc. In other words, as these things are separate in the real
world, so too they should separate in statistical models. And this ``separation
of concerns" is more parsimonious and leads to a ``cleaner", theoretically
consistent, framework.

At last, and most importantly, we must repeat that this Euclidean approach to
career matching is an oversimplification for illustrative purposes; and that we
have already developed more advanced methods to account for its problems. In
fact, it is easy to derive better matching estimates only by tweaking the model
presented above.

An immediate improvement, for example, would be to adjust weighting procedures
to further emphasize the core competencies of comparison occupations by
substituting the linear weights with a polarizing, logistic-like function. And
one could also apply scaling functions to normalized Euclidean distances, in
order to correct the similarity metric directly (e.g. by means of linear
interpolations, root functions, etc).

Having said this, beyond some ``quick fixes", more dramatic improvements
require rewriting the entire matching algorithm to another format. But then
again, the goal of this article was to provide an introduction to the crucial
issue of quantitative career matching, not to exhaust the subject. In future
works, we expect to be able to explain at length our sophisticated and
performant models.

% Conclusion
\section{Conclusion}
In this paper, we described the simplest approach to quantitative career
matching, and illustrated its application with a sample of data from a robust
source of occupational information, namely the O*NET framework. We also
discussed a few of the fundamental issues involved in assessing career path
compatibility, like competency weighting, and the problem of overqualification.
In an effort to keep the article concise and accessible, however, we
deliberately ignored many of the other complexities surrounding this subject.

Even so, we found our results to be mostly accurate, though not as precise as
they would be had we employed superior methods. We highlight that the sample
occupations were matched as ``expected": engineers with engineers; physicists
with scientists; credit analysts with other roles in the financial sector; and
dishwashers with janitors, and ``blue-collar" positions. Nevertheless, we
noted, as well, that similarity scores were too high for some of these matches.

To tackle this inconsistency, we proposed an ideal, parsimonious solution, in
which a number of independent coefficients ought to be calculated to separately
account for the various aspects affecting compatibility. In addition, we also
proposed a couple of more immediate ``quick fixes" to adjust matching
estimates.

Overall, as suggested by the article's title, this was an initial sketch to
address a most important topic: that of rationally choosing a career. And,
despite the basic model presented here not allowing to fully develop what
``picking the right occupation" looks like statistically, we do hope and think
it is, at least, a step in the right direction.

% References
\newpage
\printbibliography[
    heading=bibintoc,
    title={References}
]

% Appendix
\newpage
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
\DetailedSkillSets

\end{document}